---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
packageVersion("ggforce")
```


# **NHL.Rink**

---

## **Installation**

<!-- From CRAN (when published) -->
<!-- install.packages("NHL.Rink") -->

```{r, results = "hide", warning = FALSE, message = FALSE}
# install.packages("devtools")      
install.packages("darkghastful/NHL.Rink")
```

---

## **Quick Start**

### **Load the package**

```{r, results = "hide", warning = FALSE, message = FALSE}
library(NHL.Rink)
```

---

<!-- ### **Choose a team** -->

<!-- ```{r} -->
<!-- NHL.teams()[c(26, 22, 31),]  # Use NHL.teams() for full list -->
<!-- ``` -->

<!-- --- -->

### **Generate a rink with a team logo.**

```{r logo.rink, fig.width=6, fig.asp=85/200, dpi=900}
rink("UTA") # Use rink() for empty rink
```

---

### **NHL rink with a blues logo generated using calculated equations.**

```{r blues.rink, fig.width=6, fig.asp=85/200, dpi=300}
blues.note.plot(rink = TRUE)
```

---

## **Functions**

### `rink(team = NA)`

Generates an NHL regulation rink plot with an optional team logo.

- **Arguments**  
  - `team` — Team name, tri-code, or ID (e.g. `"STL"`).  
- **Returns**  
  - A **ggplot** object with the rink (and logo if specified).

---

### `blues.note.plot(rink = FALSE, save = FALSE)`

Calculates the equations for a Blues note logo and optionally overlays it on a rink.

- **Arguments**  
  - `rink` — Logical; if `TRUE`, overlays the note on a rink.  
  - `save` — Logical; if `TRUE`, saves as `blues.note.plot.rds` or `blues.rink.plot.rds`.  
- **Returns**  
  - A **ggplot** object of the note (and rink if `rink = TRUE`).

---

### `rink.logo(team)`

Queries and prepares a **grob** of a team logo.

- **Arguments**  
  - `team` — Team name, tri-code, or ID (e.g. `"STL"`).  
- **Returns**  
  - A **grob** that can be layered onto any ggplot.

---

## **Dependencies**

- **bqutils**  
- **ggplot2** ≥ 3.5.2  
- **ggforce**  
- **rsvg**  
- **magick**  
- **grid**  
- **stringr**  
- **magrittr**  
- **scales**

---

## **License**

GPL-3.0 license © Bailey Quinn
